Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-06 volunteer-clouds-ieee-ci-si.tex
Adds tables with initial results

Initial experiments were set up using the OpenShift
Platform-as-a-Service, which provides a free tier within which this
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August.

>>>>

Initial experiments were set up using the OpenShift
Platform-as-a-Service, which provides a free tier within which this
experiment could be performed. That way, and as required, the hardware
and cloud cost for this experiment were zero. Experiments were
announced through a post in Twitter and other social networks, and
results were published here \cite{DBLP:conf/gecco/GuervosG15}. For the
purpose of this paper, we repeated the announcement several times
through the months of April and then by the beginning of August. All
in all, we have the set of runs with the characteristics shown in
Table \ref{tab:runs}.
%
\begin{table*}
\caption{Characteristics of the volunteer computing initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|r}
\hline
Date & Number of experiments & Different IPs \\
\hline
April 4th 4/4& & 57 & 191\\
April 24th 4/24 &  231 & 559 \\
July 31th 7/31 & 97 & 179\\
\hline
\end{tabular}
\end{table}
%

\begin{table*}
\caption{Summary of time per run, number of IPS and number of {\tt
    PUT}s per IP in the initial runs. \label{tab:runs}}
\begin{center}
\begin{tabular}{l|rrr}
\hline
Date & Median IPs & Median time (s) & Median #{\tt PUT}s  \\
\hline
4/4& & 5 & 2040 & 18\\
April 24th 4/24 &  5 & 732 & 11\\
July 31th 7/31 & 5 & 260 & 23 \\
\hline
\end{tabular}
\end{table}
%
A summary of the characteristics of each run is also shown in Table
\ref{tab:summary}.
